Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-12-03 prop_letter_ajhs.tex
From: Ortiz, Gerardo Sent: Saturday, December 02, 2017 18:17 To: Tai, Yu-Tsung <yuttai@indiana.edu>; Hanson, Andrew J. <hansona@indiana.edu> Cc: Sabry, Amr A. <sabry@indiana.edu> Subject: Re: AJH typo corrections and separate major suggested edits: re: AL11679 Tai
My suggestions are:

1) Put Andy's prop_letter_ajh.tex in Sharelatex AS A SEPARATE FILE.

2) Produce a NEW file prop_letter_ajhs.tex AS ANOTHER SEPARATE FILE, and
put it ALSO in Sharelatex.

In the end there will be THREE tex files that we need to compare on
Thursday. 

   Thanks,

      Gerardo

PS: If we start mixing files we will

%% ajh - SUGGESTED INTRO SENTENCE: TEXT #0 would go here.

@@

%% ajh "begin" doubled, replace here; two missing commas
We start our investigation with the concept of $\delta$-determinism, where~$\delta$
quantifies the effect of finite-precision uncertainties on measurement
outcomes. We recast the Kochen-Specker theorem using
$\delta$-determinism to quantify the effects of finite precision and
imperfections on contextuality. When $\delta=0$, the generalized
theorem reduces to the conventional one, but as $\delta$ varies from 0
to 1 we note a transition from contextuality to non-contextuality.
% A principal result is that recasting the Kochen-Specker theorem in 
% terms of ``$\delta$-determinism,'' with~$\delta$ quantifying the 
% effect of finite-precision uncertainties on measurement outcomes, 
% reducing to the purely deterministic Kochen-Specker case for 
% $\delta=0$, can resolve the question of the effect of finite precision 
% and imperfections on contextuality.  
%% ajh kill "In more detail"
%% ajh -  LONG SUGGESTED TEXT #1 would go here
The quantum-mechanical requirement for contextuality
continues to hold, thus maintaining the Kochen-Specker result for a
\emph{non-vanishing} range of $\delta$, but that at a \emph{certain
  fixed value} of $\delta$, there is a sharp transition, parallel in
its consequences to, say, a phase transition, to
\emph{non-contextuality}. %% ; that is, suddenly a quantum system can be
%% simulated by a non-contextual hidden variable theory.
%% , turning the
%% system effectively from a quantum system into a classical system. 
% that is, quantum mechanics suddenly fails to hold, and all variables
% can be specified simultaneously, turning the theory effectively into a
% classical theory that can be specified consistently by hidden
% variables.
% \yutsung{The part after ``that is''
%   looks strange.
% \begin{enumerate}
% \item The Kochen-Specker theorem is not about quantum mechanics, is about whether
% quantum mechanics can be simulated by a non-contextual deterministic hidden
% variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
% doesn't make a lot sense.
% \item The question is whether there exist a QIVPM means ``a classical theory
% consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
% I need to check whether it qualities as a classical probabilistic hidden variable
% theory\ldots(?)
% \end{enumerate}
% }
These results provide a new insight into the Meyer-Mermin debate by
presenting a theory in which there is a \emph{parameter} interpolating
between what appeared previously to be irreconcilable aspects %interpretations
of contextuality.
% ajh- above: I think "interpretations" is not quite right -> "aspects"?

We also investigate the second key aspect of imprecise quantum
measurement, which is its statistical nature as reflected in the
application of the Born rule determining the probability of a given
measurement outcome~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
Here, Gleason's theorem establishes that there is no alternative to
the Born rule by demonstrating, using reasonable continuity arguments
in Hilbert spaces of dimension $d\ge3$, the existence of a unique
state $\rho$ consistent with the statistical predictions computed from
the Born rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
Our question then concerns what happens when infinite precision cannot
be achieved.  We are able to show that, while a QIVPM incorporating
the effects of finite precision might not be consistent with Gleason's
unique state~$\rho$ on all projectors defined on a Hilbert
space~$\Hilb$ of dimension $d\ge3$, there is a mathematically precise
sense in which one recovers the original Gleason theorem
asymptotically.  Specifically, it is possible to construct a class of
QIVPMs representing bounded resources that is parameterized by the
size of the intervals. We then demonstrate that all QIVPMs in this
class are consistent with a non-empty ``ball'' of quantum states whose
radius is defined by the maximal length of the
intervals characterizing the uncertainties. As the size of the intervals  
goes to zero, this ball of quantum states converges to a
point representing the unique state consistent with the Born rule and 
Gleason's theorem. 
%% ajh: above starting at "We then demonstrate" LONG SUGGESTED TEXT #2
%% would go here: use PLURAL, ball -> balls, and then, to me, it would
%% be better as "..converges to a dense set of points."

@@

%% ajh: Inverted logic: LONG SUGGESTED TEXT #3 would go here
A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current state of the quantum
system.  Specifically, for each pure normalized quantum
state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
$\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
generalizes to mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
induces a probability measure $\muB_{\rho}$ defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

%% ajh: big problems here: LONG SUGGESTED TEXT #5 would go here.  To
%% begin with, "axioms" is COMPLETELY undefined, appears NOWHERE in
%% the text except here.  So either NAME and LIST (instead of inline
%% text)  the several statements around Eq. (6) as axioms, or use
%% another term.  In addition the english "state of the quantum" is
%% wrong here.  Including fixing that, I would replace the first two
%% sentences by TEXT # 5.  It's really strangely written.
The above axioms describe a mathematical idealization in which the
%%state of the quantum is known and involving infinitely precise
quantum state is known and involving infinitely precise
measurements. In an actual experimental setup with an ensemble of
quantum states whose states are unknown, that are not exactly
identically prepared, and with small imperfections and inaccuracies in
measuring devices, an experimenter might only be able to determine
that the probability of an event $P$ is concentrated in the range
$[0.49,0.51]$ instead of being precisely $0.5$. The spread in this
range depends on the amount of resources (time, energy, money, etc.)
that are devoted to the experiment. In the classical setting, this
``fuzziness'' can be formalized by moving to \emph{interval-valued
  probability measures} (IVPMs), which we explore in the next section,
along with our proposed extension to the quantum domain.

@@

%% ajh: inverted logic and phrasing.  I would start at "To formalize
%% this ..." and replace all the way to Eq (9) by LONG SUGGESTED TEXT
%% #6,  which coherently introduces the "core" and sets if off as a
%% DEFINITION, etc. 
We now show that our definition of QIVPMs is consistent with classical
IVPMs in the sense that a restriction of QIVPMs to mutually commuting
events recovers the definition of classical IVPMs. To formalize this
connection, we first note that in contrast to the case with
conventional quantum probability spaces, there is generally no unique
state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
is \emph{consistent} with a state $\rho$ and projector~$P$ if the
interval $\bar{\mu}(P)$ contains the exact probability calculated by
the Born rule, i.e, if:
\begin{equation}
\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)$
is the probability of the event~$P$ as determined by the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

%%ajh: This story order is incomprehensible.  In my suggested
%% replacement: LONG SUGGESTED TEXT #7, I would state FIRST that 'here
%% is the outline of the proof', and LAST 'Thm 1..., whose full proof
%% will appear in [44].
The proof that QIVPMs become classical IVPMs when the space of events
includes only mutually commuting events is presented in detail in a
forthcoming thesis~\cite{TaiThesis2018}. The idea of the proof is as
follows. Given a subspace of mutually commuting events~$\eventsC$, we
can construct a partial orthonormal basis by diagonalization and
complete it to a full orthonormal basis $\overline{\eventsC}$. We then
build a bijection between the QIVPM on the set of projectors
associated with this basis and the set of classical events
corresponding to this basis. Using this correspondence together with a
classical result by
Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
we can establish that for the special case of commuting events, a
QIVPM will always have a non-empty core~\footnote{Shapley's result
  proves that a classical IVPM always contains at least one state that
  is consistent with every event.}.

@@

%% ajh - inverted narrative order, suggested fix in 
%%   LONG SUGGESTED TEXT #8 would go here
The importance of this property is that it is violated in
finite-precision versions of Gleason's theorem
(cf. Thm.~\ref{thm:Non-extensible-of-Gleason's} in Sec.~\ref{sec:Gleason}). As we will show, the set of states
$\coreBorn\left(\bar{\mu},\events'\right)$ that is consistent with
some arbitrary (not necessarily commuting) events~$\events'$ and a
particular QIVPM $\bar{\mu}$ may be \emph{empty}.

>>>>

\andy{TEXT \#0 would go here.}
  In this investigation, we explore the implications of extending
  point-like quantum-mechanical probability measures to finite
  intervals. 
\andy{End of TEXT \#0}

@@

%% ajh "begin" doubled, replace here; two missing commas
We start our investigation with the concept of $\delta$-determinism, where~$\delta$
quantifies the effect of finite-precision uncertainties on measurement
outcomes. We recast the Kochen-Specker theorem using
$\delta$-determinism to quantify the effects of finite precision and
imperfections on contextuality. When $\delta=0$, the generalized
theorem reduces to the conventional one, but as $\delta$ varies from 0
to 1 we note a transition from contextuality to non-contextuality.
% A principal result is that recasting the Kochen-Specker theorem in 
% terms of ``$\delta$-determinism,'' with~$\delta$ quantifying the 
% effect of finite-precision uncertainties on measurement outcomes, 
% reducing to the purely deterministic Kochen-Specker case for 
% $\delta=0$, can resolve the question of the effect of finite precision 
% and imperfections on contextuality.  
%% ajh kill "In more detail"
\andy{TEXT \#1 would go here}
quantum-mechanical contextuality continues to hold, maintaining the 
Kochen-Specker result, but at a   \emph{certain fixed value} of
$\delta$, there is a sharp transition to   \emph{non-contextuality},
parallel in character to, say, a  phase transition.
These results provide a new insight into the Meyer-Mermin debate by
presenting a theory in which there is a \emph{parameter} interpolating
between what appeared previously to be irreconcilable aspects
of contextuality.
\andy{End of \#1}
The quantum-mechanical requirement for contextuality
continues to hold, thus maintaining the Kochen-Specker result for a
\emph{non-vanishing} range of $\delta$, but that at a \emph{certain
  fixed value} of $\delta$, there is a sharp transition, parallel in
its consequences to, say, a phase transition, to
\emph{non-contextuality}. %% ; that is, suddenly a quantum system can be
%% simulated by a non-contextual hidden variable theory.
%% , turning the
%% system effectively from a quantum system into a classical system. 
% that is, quantum mechanics suddenly fails to hold, and all variables
% can be specified simultaneously, turning the theory effectively into a
% classical theory that can be specified consistently by hidden
% variables.
% \yutsung{The part after ``that is''
%   looks strange.
% \begin{enumerate}
% \item The Kochen-Specker theorem is not about quantum mechanics, is about whether
% quantum mechanics can be simulated by a non-contextual deterministic hidden
% variable theory or not. Hence, ``quantum mechanics suddenly fails to hold''
% doesn't make a lot sense.
% \item The question is whether there exist a QIVPM means ``a classical theory
% consistently by hidden variables.'' At least, a QIVPM is not deterministic, and
% I need to check whether it qualities as a classical probabilistic hidden variable
% theory\ldots(?)
% \end{enumerate}
% }
These results provide a new insight into the Meyer-Mermin debate by
presenting a theory in which there is a \emph{parameter} interpolating
between what appeared previously to be irreconcilable aspects %interpretations
of contextuality.
% ajh- above: I think "interpretations" is not quite right -> "aspects"?

We also investigate the second key aspect of imprecise quantum
measurement, which is its statistical nature as reflected in the
application of the Born rule determining the probability of a given
measurement outcome~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
Here, Gleason's theorem establishes that there is no alternative to
the Born rule by demonstrating, using reasonable continuity arguments
in Hilbert spaces of dimension $d\ge3$, the existence of a unique
state $\rho$ consistent with the statistical predictions computed from
the Born rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.
Our question then concerns what happens when infinite precision cannot
be achieved.  We are able to show that, while a QIVPM incorporating
the effects of finite precision might not be consistent with Gleason's
unique state~$\rho$ on all projectors defined on a Hilbert
space~$\Hilb$ of dimension $d\ge3$, there is a mathematically precise
sense in which one recovers the original Gleason theorem
asymptotically.  Specifically, it is possible to construct a class of
QIVPMs representing bounded resources that is parameterized by the
size of the intervals. We then demonstrate that all QIVPMs in this
class are consistent with a non-empty ``ball'' of quantum states whose
radius is defined by the maximal length of the
intervals characterizing the uncertainties. As the size of the intervals  
goes to zero, this ball of quantum states converges to a
point representing the unique state consistent with the Born rule and 
Gleason's theorem. 
\andy{TEXT \#2 would go here}
We then demonstrate that all QIVPMs in this class are
consistent with non-empty ``balls'' of quantum states whose radii
correspond to the lengths of the intervals characterizing the
uncertainties.  As the sizes of the intervals go to zero, these balls
of quantum states converge to a dense, continuous, set of points
representing the unique states consistent with the Born rule and
Gleason's theorem.
\andy{End of TEXT \#2}
%% ajh: above starting at "We then demonstrate" LONG SUGGESTED TEXT #2
%% would go here: use PLURAL, ball -> balls, and then, to me, it would
%% be better as "..converges to a dense set of points."

@@

%% ajh: Inverted logic: LONG SUGGESTED 
\andy{TEXT \#3 would go here}
A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current state of the quantum
system.  Specifically, for each pure normalized quantum
state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
$\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
generalizes to mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
induces a probability measure $\muB_{\rho}$ defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.
\andy{End of TEXT \#3}
A conventional quantum probability measure can easily be constructed
using the Born rule if one knows the current state of the quantum
system.  Specifically, for each pure normalized quantum
state~$\ket{\phi} \in {\cal H}$, the Born rule induces a probability measure
$\muB_{\phi}$ defined as
$\muB_{\phi}(P)=\melem{\phi}{P}{\phi}$. The situation
generalizes to mixed states
$\rho = \sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$, where $\ket{\phi_j} \in {\cal H}$, $q_j > 0$, and
$\sum_{j=1}^{N}q_{j}=1$, in which case the generalized Born rule
induces a probability measure $\muB_{\rho}$ defined as
$\muB_{\rho}\left(P\right) = \Tr\left(\rho P\right) =
\sum_{j=1}^{N}
q_{j}\muB_{\phi_{j}}\left(P\right)$~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

%% ajh: big problems here: LONG SUGGESTED 
\andy{TEXT \#5 would go here.}
The above construction assumes a mathematical idealization
having known quantum state and infinitely precise measuring
instruments.  In an actual experimental setup with an ensemble of
quantum states that would ideally be identical, but are not actually
identically prepared, with imperfections and inaccuracies in the
measuring devices,  an experimenter might only be able to determine
that the probability of an event $P$ is concentrated in the range
$[0.49,0.51]$ instead of being precisely $0.5$.   The spread in this
range depends on the amount of resources (time, energy, money, etc.)
that are devoted to the experiment.  In the classical setting, this
``fuzziness'' can be formalized by moving to \emph{interval-valued
  probability measures} (IVPMs), which we explore in the next section,
along with our proposed extension to the quantum domain.
\andy{End of TEXT \#5}
%% To
%% begin with, "axioms" is COMPLETELY undefined, appears NOWHERE in
%% the text except here.  So either NAME and LIST (instead of inline
%% text)  the several statements around Eq. (6) as axioms, or use
%% another term.  In addition the english "state of the quantum" is
%% wrong here.  Including fixing that, I would replace the first two
%% sentences by TEXT # 5.  It's really strangely written.
The above axioms describe a mathematical idealization in which the
%%state of the quantum is known and involving infinitely precise
quantum state is known and involving infinitely precise
measurements. In an actual experimental setup with an ensemble of
quantum states whose states are unknown, that are not exactly
identically prepared, and with small imperfections and inaccuracies in
measuring devices, an experimenter might only be able to determine
that the probability of an event $P$ is concentrated in the range
$[0.49,0.51]$ instead of being precisely $0.5$. The spread in this
range depends on the amount of resources (time, energy, money, etc.)
that are devoted to the experiment. In the classical setting, this
``fuzziness'' can be formalized by moving to \emph{interval-valued
  probability measures} (IVPMs), which we explore in the next section,
along with our proposed extension to the quantum domain.

@@

%% ajh: inverted logic and phrasing.  I would start at "To formalize
%% this ..." and replace all the way to Eq (9) by LONG SUGGESTED 
\andy{TEXT \#6}
We now show that our definition of QIVPMs is consistent
with classical IVPMs in the sense that a restriction of QIVPMs to
mutually commuting events recovers the definition of classical
IVPMs.  However, we must refine this context for the quantum case,
defining a QIVPM  $\bar{\mu}$ to be \emph{consistent} with a state $\rho$ and
projector~$P$ if the interval $\bar{\mu}(P)$ contains the exact
probability calculated by the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007} , i.e, if:

 To formalize this connection, we first note that in contrast to
the case with conventional quantum probability spaces, there is
generally no unique state~$\rho$ consistent with a QIVPM. We say that
a QIVPM $\bar{\mu}$ is \emph{consistent} with a state $\rho$ and
projector~$P$ if the interval $\bar{\mu}(P)$ contains the exact
probability calculated by the Born rule,
  \begin{equation}
  \muB_{\rho}\left(P\right) = \Tr\left(\rho
  P\right)\in\bar{\mu}\left(P\right)\ .
  \end{equation}
In contrast with conventional probability spaces, there is \emph{no
guarantee} that a unique state $\rho$ consistent with a QIVPM exists.

  We next refine the concept of consistency by introducing the idea of
a ``core'' set of states relative to subspaces. First, we define
$\events'$ as a \emph{subspace} of a set of events if $\events$ if
$\events'$ contains  $\mathbb{0}$ and $\mathbb{1}$ and is closed under
complements, sums, and products.  In particular, for any
projector~$P\in\events'$, we have
$\mathbb{1}-P\in\events'$ and for each pair of commuting
projectors~$P_{0}\in\events'$ and $P_{1}\in\events'$, we have
$P_{0}+P_{1}-P_{0}P_{1}$ and $P_{0}P_{1}\in\events'$.

\begin{definition}[The core of a probability measure] The \emph{core}
$\coreBorn\left(\bar{\mu},\events'\right)$ of a probability measure 
$\bar{\mu}$ relative to a subspace of events $\events'$ is the
collection of all states $\rho$ that are \emph{consistent} with 
$\bar{\mu}$ on every projector in $\events'$, that is
\begin{equation}
\label{eq:hbar}
\coreBorn\left(\bar{\mu},\events'\right) = \set{\rho}{\forall P\in
\events',~\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)} \ .
\end{equation}
\end{definition}
\andy{End of TEXT \#6}
%% which coherently introduces the "core" and sets if off as a
%% DEFINITION, etc. 
We now show that our definition of QIVPMs is consistent with classical
IVPMs in the sense that a restriction of QIVPMs to mutually commuting
events recovers the definition of classical IVPMs. To formalize this
connection, we first note that in contrast to the case with
conventional quantum probability spaces, there is generally no unique
state~$\rho$ consistent with a QIVPM. We say that a QIVPM $\bar{\mu}$
is \emph{consistent} with a state $\rho$ and projector~$P$ if the
interval $\bar{\mu}(P)$ contains the exact probability calculated by
the Born rule, i.e, if:
\begin{equation}
\muB_{\rho}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\muB_{\rho}\left(P\right)=\Tr\left(\rho P\right)$
is the probability of the event~$P$ as determined by the Born
rule~\citep{Born1983bibTeX,Mermin2007,Jaeger2007}.

@@

%%ajh: This story order is incomprehensible.  In my suggested
%% replacement: LONG SUGGESTED 
\andy{TEXT \#7}
   The general idea of the proof that QIVPMs become classical
IVPMs when the space of events includes only mutually commuting
events depends on showing the existence of a non-empty core for such
commuting events.  The first step in establishing this assertion is to
to take a subspace $\eventsC$ of mutually commuting events, construct
a partial orthonormal basis by diagonalization, and complete this to a
full orthonormal basis  $\overline{\eventsC}$.  We then
build a bijection between the QIVPM on the set of projectors
associated with this basis and the set of classical events
corresponding to this basis.  Using this correspondence together with a
classical result by
Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
we can establish that for the special case of commuting events, a
QIVPM will always have a non-empty core~\footnote{Shapley's result
  proves that a classical IVPM always contains at least one state that
  is consistent with every event.}.  This leads to
\begin{thm}[Non-empty Core for Compatible Measurements] \label{thm:Shapley}
  For every QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
  of events~$\eventsC\subseteq\events$ commutes, then
  $\coreBorn\left(\bar{\mu},\eventsC\right)\ne\emptyset$,
\end{thm}
whose full proof will appear in ~\cite{TaiThesis2018}.
\andy{End of TEXT \#7}
%% I would state FIRST that 'here
%% is the outline of the proof', and LAST 'Thm 1..., whose full proof
%% will appear in [44].
The proof that QIVPMs become classical IVPMs when the space of events
includes only mutually commuting events is presented in detail in a
forthcoming thesis~\cite{TaiThesis2018}. The idea of the proof is as
follows. Given a subspace of mutually commuting events~$\eventsC$, we
can construct a partial orthonormal basis by diagonalization and
complete it to a full orthonormal basis $\overline{\eventsC}$. We then
build a bijection between the QIVPM on the set of projectors
associated with this basis and the set of classical events
corresponding to this basis. Using this correspondence together with a
classical result by
Shapley~\cite{Shapley1971,GilboaSchmeidler1994,NgMoYeh1997,Grabisch2016},
we can establish that for the special case of commuting events, a
QIVPM will always have a non-empty core~\footnote{Shapley's result
  proves that a classical IVPM always contains at least one state that
  is consistent with every event.}.

@@

%% ajh - inverted narrative order, suggested fix in 
%%   LONG SUGGESTED 
\andy{TEXT \#8 would go here}
The importance of the existence of empty cores combined with
  the conditions guaranteeing non-empty cores is that one cannot
  guarantee non-empty cores for finite-precision attempts at proving
  Gleason's theorem by extending the Born measure
  $\muB_{\rho}\left(P\right)$ to QIVPMs $\bar{\mu}\left(P\right)$.  We
  will show in  Sec.~\ref{sec:Gleason} that a core defined by the set
  of states $\coreBorn\left(\bar{\mu},\events'\right)$ that is
  consistent with some arbitrary (not necessarily commuting)
  events~$\events'$  and a particular QIVPM  $\bar{\mu}$
   \emph{may be empty}.
\andy{End of TEXT \#8}
The importance of this property is that it is violated in
finite-precision versions of Gleason's theorem
(cf. Thm.~\ref{thm:Non-extensible-of-Gleason's} in Sec.~\ref{sec:Gleason}). As we will show, the set of states
$\coreBorn\left(\bar{\mu},\events'\right)$ that is consistent with
some arbitrary (not necessarily commuting) events~$\events'$ and a
particular QIVPM $\bar{\mu}$ may be \emph{empty}.
